Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-05-08 docs/mixture_models.tex
galfit
references

% to-do
% -----
% - zeroth draft
% - make useful figures
% - send to Jim Bosch and Kevin Bundy for comments

@@

\newcommand{\foreign}[1]{\textit{#1}}
\newcommand{\etal}{et\,al.}
\newcommand{\documentname}{\textsl{Note}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\tractor}{\project{Tractor}}
\newcommand{\sdss}{\project{SDSS}}

@@

We are not the first in this space....modeling galaxies with mixtures
of Gaussians has been done very successfully before [HOGG cite].
However, the idea behind that work was to use the mixture of Gaussians
to provide a very free form for the isophotes of large, nearby, highly
resolved galaxies.  Here our goals are very limited: We want to
improve the performance of standard galaxy image model fitting by
expressing the standard galaxy models---the exponential and
de~Vaucouleurs profiles---as rigid mixtures of Gaussians.

@@

@@

\begin{thebibliography}{70}
\bibitem[Bovy \etal(2011a)]{xd}
Bovy,~J., Hogg,~D.~W., \& Roweis,~S., 2011, Ann. Appl. Stat., 5, 1657
\bibitem[Bovy \etal(2011b)]{xdqso}
Bovy,~J., \etal, 2011, \apj, 729, 141
\bibitem[Bovy \etal(2012)]{xdqsoz}
Bovy,~J. \etal, 2012, \aj, 749, 41
\end{thebibliography}

>>>>

% to-do
% -----
% - write zeroth draft
% - make useful figures
% - send to Jim Bosch and Kevin Bundy for comments

@@

\newcommand{\foreign}[1]{\textit{#1}}
\newcommand{\etal}{\foreign{et\,al.}}
\newcommand{\documentname}{\textsl{Note}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\tractor}{\project{Tractor}}
\newcommand{\sdss}{\project{SDSS}}

@@

We are not the first in this space deconvolution and modeling of
galaxy images with mixtures of Gaussians has been done very
successfully before \citep[for example,][]{bendinelli, emsellem,
  bendinelli2, cappellari}.  However, the idea behind those projects
was to use the mixture of Gaussians to provide a very free form for
the isophotes or morphologies of resolved galaxies or other complex
scenes.  Here our goals are very limited: We want to improve the
performance of standard galaxy image model fitting by expressing the
standard galaxy models---the exponential and de~Vaucouleurs
profiles---as rigid mixtures of Gaussians.

@@

...somehow have to cite GALFIT \citep{galfit} in this section...

@@

\begin{thebibliography}{70}
\bibitem[Bendinelli(1991)]{bendinelli}
Bendinelli,~O., 1991, \apj, 366, 599
\bibitem[Bendinelli \& Parmeggiani(1995)]{bendinelli2}
Bendinelli,~O. \& Parmeggiani,~G., 1995, \aj, 109, 572
\bibitem[Bovy \etal(2011a)]{xd}
Bovy,~J., Hogg,~D.~W., \& Roweis,~S., 2011, Ann. Appl. Stat., 5, 1657
\bibitem[Bovy \etal(2011b)]{xdqso}
Bovy,~J., \etal, 2011, \apj, 729, 141
\bibitem[Bovy \etal(2012)]{xdqsoz}
Bovy,~J. \etal, 2012, \aj, 749, 41
\bibitem[Cappellari(2002)]{cappellari}
Cappellari,~M., 2002, \mnras, 333, 400
\bibitem[Emsellem \etal(1994)]{emsellem}
Emsellem,~E., Monnet,~G., Bacon,~R., \& Nieto,~J.-L., 1994, \aap, 285, 739
\bibitem[Peng \etal(2002)]{galfit}
Peng,~C.~Y., Ho, L.~C., Impey,~C.~D., \& Rix,~H.-W., 2002, \aj, 124, 266
\end{thebibliography}
